Software Clusterings with Vector Semantics and the Call Graph

### 2019-08-23 slides/slides.tex
Update slides

\institute[BaLab]{BALab, Athens University of Economics and Bussiness \\ National Technical University of Athens \\ Advisor: Prof. Diomidis Spinellis}
\date[ESEC/FSE 2019 SRC]{Student Research Competition \\ ESEC/FSE August 2019 \\ Estonia}

@@

$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j))}$$

@@

    where $\Sigma_{in}$ is sum of all the weights of the links inside the community $i$ is moving into, $\Sigma_{tot}$ is the sum of all the weights of the links to nodes in the community $i$ is moving into, $k_{in} (i)$ is the sum of the weights of the links between $i$ and other nodes in the community that $i$ is  moving into.

    \item<5-> The communities that Louvain Clustering produces

@@

The MoJo \cite{mojo} metric is a clustering distance metric used for comparing software clusterings. The MoJo distance between two clusterings $\mathcal C_1, \mathcal C_2$ is defined as the minimum number of moves and joins to transform one clustering to another where 
\begin{itemize}
    \item<1-> \textbf{Move:} Moving a resource from one cluster to another (that includes moving a resource into a previously nonexistent cluster or creating a new cluster.
    \item<2-> \textbf{Join:} Join two clusters into one.
	\item<3-> The MoJo distance is therefore defined as

@@

\begin{itemize}
    \item Average Linkage\footnote{$w(A, B) = \sum_{a \in A, b \in B} w(a,b)$}  $\mathrm{argmax}_{A, B} \frac {w(A, B)}{|A||B|}$
    \item Complete Linkage $\mathrm{argmax}_{a \in A, b \in B} w(a, b)$
    \item Single Linkage $\mathrm{argmin}_{a \in A, b \in B} w(a, b)$
    \item Ward Linkage 
    \item Information Loss (Agglomerative Information Bottleneck Algorithm)
\end{itemize}

@@

\begin{itemize}
	\item LIMBO
	\item ACDC

@@

\begin{frame}{Results}

    \begin{table}
    \Tiny
    \begin{tabular}{lrrrrrrr}
    \hline
    Alg. & Dim.  & $n_c$ & Range & $\bar x$ & $\sigma$ & Median & Dist. \\
    \hline
    \textsc{acdc}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
    Average Linkage  & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
    Complete Linkage  & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
    \textsc{limbo}  \footnote{($B=100, \; S = \infty$)} & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\

    Ward Linkage\footnote{Eucledian Affinity} & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\

    \textsc{sade} & \emph{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10) & 243 ($\pm$ 1)  \\
    \textsc{sade} (Directed) & \emph{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)  & 237 ($\pm$ 2) \\
    \hline
    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
    \hline
  \end{tabular}
    \caption{Experimental Results for Linux 4.21. Italics denote manually defined parameters}

@@

\begin{itemize}
    %\item Testing our system with various codebases to validate method's generalizability
    \item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
    \item Integration with more static analyzers 
\end{itemize}

>>>>

\institute[BaLab/NTUA]{BALab, Athens University of Economics and Bussiness \\ National Technical University of Athens \\ Advisor: Prof. Diomidis Spinellis}
\date[ESEC/FSE 2019 SRC]{Student Research Competition \\ ESEC/FSE 2019, Tallin \\ ACAC 2019, Athens}

@@

$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j))} \qquad s(w_c, w_t) = \langle \vec d_c, \vec d_t \rangle$$

@@

    where $\Sigma_{in}$ is sum of all the weights of the links inside the community $i$ is moving into, $\Sigma_{tot}$ is the sum of all the weights of the links to nodes in the community $i$ is moving into, $k_{in} (i)$ is the sum of the weights of the links between $i$ and other nodes in the community that $i$ is  moving into.
	\item<5-> This measure determines \textbf{how much the modularity changes via moving (joining) community $i$ with community $j$}. At each round, these values are calculated for the community $i$ and its neighboring communities and $i$ is merged with $j^* \in \mathrm{argmax}_{j \in N(i)} \{ \Delta Q(i, j) \}$

	\item<6-> Runs in time $O(n \log n)$

@@

The MoJo \cite{mojo} metric is a clustering distance metric used for comparing software clusterings. The MoJo distance between two clusterings $\mathcal C_1, \mathcal C_2$ is defined as the \textbf{minimum number of moves and joins} to transform one clustering to another where 
\begin{itemize}
    \item<1-> \textbf{Move:} Moving a resource from one cluster to another (that includes moving a resource into a previously nonexistent cluster or creating a new cluster.
    \item<2-> \textbf{Join:} Join two clusters into one.
	\item<3-> The MoJo distance is therefore defined as

@@

\begin{itemize}
    \item Average Linkage\footnote{$w(A, B) = \sum_{a \in A, b \in B} w(a,b)$}  $\mathrm{argmax}_{A, B} \frac {w(A, B)}{|A||B|}$
    \item Complete Linkage $\mathrm{argmax}_{a \in A, b \in B} w(a, b)$
    \item Single Linkage $\mathrm{argmin}_{a \in A, b \in B} w(a, b)$
    \item Ward Linkage. Ward minimizes $J(C) = \sum_{\vec x, \vec y \in C} \| \vec x - \vec y \|^2$ for each cluster $C \in \mathcal C$. 
    \item Information Loss (Agglomerative Information Bottleneck Algorithm)
\end{itemize}

@@

\begin{itemize}
	\item LIMBO: Clusters modules upon inserting their Distributional Cluster
Features to a B+-tree variant and then applying the Agglomerative
Information Bottleneck algorithm.\footnote{aka Agglomerative Clustering with Mutual Information Loss as Measure} 
	\item ACDC: Leans toward to software components comprehension
based on subsystem patterns.

@@

\begin{frame}[allowframebreaks]
    \frametitle{Results}
    \tiny
    \begin{table}

    \begin{tabular}{lrrrrrrr}
    \hline
    Method & Dim.  & $n_c$ & Range & $\bar x$ & $\sigma$ & Median  \\
    \hline
    \textsc{acdc}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 \\
    Average Linkage  & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 \\
    Complete Linkage  & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 \\
    \textsc{limbo}   & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50 \\

    Ward Linkage & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 \\

    \textsc{sade} & \emph{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10)   \\
    \textsc{sade} (Directed) & \emph{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)   \\
    \hline
    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 \\
    \hline
  \end{tabular}
   \caption{Experimental Results for Linux 4.21. Italics denote manually defined parameters}

  \begin{table}
  \framebreak
  \small
  \begin{tabular}{lr}
    \hline
    Method &   MoJo Distance \\
    \hline
    \textsc{acdc}  &  33694\\
    Average Linkage  & 2092 \\
    Complete Linkage  &  1710 \\
    \textsc{limbo}  \footnote{($B=100, \; S = \infty$) and Bag-of-Words Features} &  1482 \\

    Ward Linkage\footnote{Eucledian Affinity} &  1138 \\

    \textsc{sade} &  243 ($\pm$ 1)  \\
    \textsc{sade} (Directed) &  237 ($\pm$ 2) \\ \hline

    \end{tabular}
    \caption{MoJo Distances}

@@

\begin{itemize}
    \item Testing our system with various codebases (e.g. gcc, Postgres etc.)
    %\item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
    \item Integration with more static analyzers 
    \item Propose layered software architectures
\end{itemize}
